DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
reviewed experimental evaluation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox, but applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
To the best of our knowledge, there is no MATLAB toolbox able to perform digital controller synthesis based on 
program synthesis engines that considers the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

@@

Our experimental evaluation consists of $18$ SISO control system benchmarks 
extracted from the literature~\cite{abate2017, abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
voltage regulator, and an acrobot control system.

@@

>>>>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox, but applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
To the best of our knowledge, there is no MATLAB toolbox able to perform digital controller synthesis based on 
program synthesis engines that considers the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

@@

Our experimental evaluation consists of $18$ SISO control system benchmarks 
extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
voltage regulator, and an acrobot control system.

@@

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer function or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

Additionally, we are able to reproduce the stability for all evaluated control system benchmarks.
As an example, we have reproduced the stability property in the synthesized controller 
for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
in MATLAB. Fig.~\ref{tf-step-response} shows that the digital controller 
synthesized by the \tool stabilizes the closed-loop control system using 
the series connection (as shown in Fig.~\ref{fig:typical-control-system}) for the DC motor plant. 
We have applied this procedure to all synthesized controllers to confirm the reliability of our experimental results.
%
\begin{equation}
\label{tf-synth-controller}
C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
  \label{tf-step-response}
\end{figure}

Regarding the state-space representation, we can check the physical plant expressed by 
Eq.~\eqref{ss-synth-controller} (describing a pendulum control system), that the feedback matrix 
(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the physical plant 
with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
%
\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

Where,
%
$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$

\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
  \label{ss-step-response}
\end{figure}

The synthesized controllers are validated to be stable using the MATLAB step reponse, 
which means that our results are reliable for control engineers. A link to the full experimental environment, 
including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website.\footnote{\url{www.dsverifier.org}}
